Region-network hierarchical sparsity priors for\\ high-dimensional inference in brain imaging

### 2016-01-28 paper/paper.tex
first abstract

\begin{abstract}
% Imaging neuroscience links human behavior to aspects of brain
% biology in ever-increasing datasets.

>>>>

\begin{abstract}
Structured sparsity penalization has recently improved
statistical models applied to high-dimensional data in various domains.
As an extension to neuroscience,
network hierarchies of brain regions have been incorporated as priors into
brain imaging analysis.
This remarries the inextricable perspectives of
functional segregation and functional integration
that are routinely divorced in neuroscientific research.
%
Region-network hierarchical priors for logistic regression classification
in a reference dataset are
shown to outperform na\"ive $\ell_1$-norm and
trace-norm penalization, as well as neurobiologically
informed $\ell_1/\ell_2$-block-norm group sparsity.
Varying the relative importance of
region and network structure within the hierarchical tree prior
recovered complementary aspects of the neural activity pattern
with similar predictive accuracies.
%
In sum,
we demonstrate that priors of local and global neurobiological knowledge can enhance
out-of-sample performance and domain interpretability
by structed sparsity principles.
